Is essentiality of genes conserved in Enterobacteriaceae?

### 2017-03-15 documents/manuscript.tex
Corrected the annotations and reran the codes, listed some candidate genes for further study

\subsection{Phylogenetic analysis of gene essentiality identifies that essential genes are more likely to be conserved}
When a mutation is introduced to a gene, the fixation rate depends on how tolerable this mutation is \cite{wilson_biochemical_1977}. As mutations in essential genes are less likely to be tolerable, less mutations should be fixed in these genes, and therefore essential genes should evolve more slowly than non-essential genes. This is known as knockout rate hypothesis \cite{krylov_gene_2003}. Different studies have verified this hypothesis in prokaryotes \cite{jordan_essential_2002, gerdes_experimental_2003, rocha_analysis_2004, silander_constancy_2009}.

>>>>

\subsection{Phylogenetic analysis of gene essentiality identifies that essential genes are more likely to be conserved}
%When a mutation is introduced to a gene, the fixation rate depends on how tolerable this mutation is \cite{wilson_biochemical_1977}. As mutations in essential genes are less likely to be tolerable, less mutations should be fixed in these genes, and therefore essential genes should evolve more slowly than non-essential genes. This is known as knockout rate hypothesis \cite{krylov_gene_2003}. Different studies have verified this hypothesis in prokaryotes \cite{jordan_essential_2002, gerdes_experimental_2003, rocha_analysis_2004, silander_constancy_2009}.
